### 2014-09-06 introduction.tex
intro, typos done

Recently, a novel kind of analysis called predictive analysis~\cite{yannis,pldi14,Said:2011} was proposed. It has the capabilities of 
achieving soundness as dynamic analyses and reasoning about properties that did not occur during execution 
just like in static analysis. The basic idea is to leverage dynamic analysis to provide the information that 
is difficult to acquire through static analysis, such as a complex execution path that covers important functionalities 
and aliasing information. Note that during execution, we know precisely which write access reaches any given read 
access. While such information is encoded in a trace, predictive analysis reasons about mutation of the trace to 
expose problems or study properties that may not manifest during execution. It was used in sound data race detection. 
In particular, it collects a trace of threaded execution that contains rich runtime information such as concrete values, 
execution path, and memory accesses. It then leverages constraint solving to reason about if races can occur with
a different thread schedule, {\em while enforcing the critical runtime information (e.g. values, thread
local paths, and memory accesses) remains the same during schedule perturbation}. The rationale is that 
it becomes as difficult as static analysis if we allow these critical runtime information change. 
Predictive analysis has been shown to be very effective. It can detect real data races from complex programs.
And more importantly, it guarantees the results are sound (i.e. no false positives).

@@

However, we observe that such restrictions are unnecessary. For example, we can allow line {\tt 4} to receive its
value from line {\tt 1} as it has the same effect on thread local execution (i.e. the same branch is taken). 
This relaxation would allow us to execute lines {\tt 4} and {\tt 5} before line {\tt 2}, thereby exposing 
the first missing race. We can also allow the trace to take the else branch such that the second race is also exposed. 
Note that even though that branch was not executed originally, its effect can be precisely modeled as the value 
of $x$ is known from the original trace. As such, we can still perform sound analysis.

>>>>

Recently, a novel kind of analysis called predictive analysis~\cite{yannis,pldi14,Said:2011} was proposed. It has the capabilities of 
achieving soundness as dynamic analyses and reasoning about properties that did not occur during the execution 
just like in static analysis. The basic idea is to leverage dynamic analysis to provide the information that 
is difficult to acquire through static analysis, such as a complex execution path that covers important functionalities 
and aliasing information. Note that during execution, we know precisely which write access reaches any given read 
access. While such information is encoded in a trace, predictive analysis reasons about mutation of the trace to 
expose problems or study properties that may not manifest during execution. It was used in sound data race detection. 
In particular, it collects a trace of threaded execution that contains rich runtime information such as concrete values, 
execution path, and memory accesses. It then leverages constraint solving to reason about if races can occur with
a different thread schedule, {\em while enforcing the critical runtime information (e.g. values, thread
local paths, and memory accesses) remains the same during schedule perturbation}. The rationale is that 
it becomes as difficult as static analysis if we allow these critical runtime information change. 
Predictive analysis has been shown to be very effective. It can detect real data races from complex programs.
And more importantly, it guarantees the results are sound (i.e. no false positives).

@@

However, we observe that such restrictions are unnecessary. For example, we can allow line {\tt 4} to receive its
value from line {\tt 1} as it has the same effect on thread local execution (i.e. the same branch is taken). 
This relaxation would allow us to execute lines {\tt 4} and {\tt 5} before line {\tt 2}, thereby exposing 
the first missing race. We can also allow the trace to take the else branch such that the second race is also exposed. 
Note that even though that branch was not executed originally, its effect can be precisely modeled as the address 
of $x$ is known from the original trace. As such, we can still perform sound analysis.
